Supplement to ``{\mytitle}''

### 2023-08-29 si/si.Rnw
minor edit

We do not see any immediate reason that this model could not be extended to cover a larger range of the data, and chose the value $t_0 = \text{2010-11-13}$.
This choice of $t_0$ corresponds to using approximately $1\%$ of the available data to determine initial values of the latent states.
In addition to modeling a larger portion of the available data, this choice of $t_0$ corresponds to an important real-world event, as daily reports from each of the departments were not being sent to the health ministry until November 10, 2010; % TODO: Cite
this choice of $t_0$ therefore makes $\bm{Y}\big(t_1\big)$ the first week of complete data.

@@

While
In order to retain a similar model for the initial values of the latent state, it was necessary to pick a value of $t_0$ that was greater than 2010-10-23 (the first available data points).

>>>>

We do not see any immediate reason that this model could not be extended to cover a larger range of the data, and chose the value $t_0 = \text{2010-11-13}$.
This choice of $t_0$ corresponds to using approximately $1\%$ of the available data to determine initial values of the latent states.
In addition to modeling a larger portion of the available data, this choice of $t_0$ corresponds to an important real-world event, as daily reports from each of the departments were not being sent to the health ministry until November 10, 2010; % TODO: Cite
this choice of $t_0$ therefore makes $\bm{Y}\big(t_1\big)$ the first week of data once daily reports are being sent to the health ministry.

@@
